### 2022-01-09 src-latex/parts/50-xp-setup.tex
more details in setup and results

\subsection{Training procedure}
5-fold CV for all models.
\begin{itemize}
\item Spacy CNN : no limits on the number of epochs, instead use patience=1600.
\item CamemBERT : 3 epochs.
\end{itemize}

@@

\subsection{Implementation details}
we use spacy \mcite{spacy}
will we use FLAIR as well?

>>>>

\subsection{Training procedure}

\begin{itemize}
\item All : leave out 3 directories (~20\% of the dataset) as test data. Then apply stratified sampling based on the directory of each entry to split the remaining into a train set (~72\%) and a dev set (~8\%).
\item Spacy CNN : No limit on epochs, instead use patience 1600.
\item CamemBERT \& CamemBERT pretrained : 3 epochs.
\end{itemize}

Experiment 1: split the training set in half recursively as long as the train \& dev sets contain at least one entry of each directory in the original trainset. On the current dataset with 8k entries this leads to the creations of 8 subsets containing 0.8, 1.5, 3.1, 6.2, 12.5, 25, 50 and 100\% of the full train set. Models arerun 5 times on each trainset.

Experiment 2 : 1 run per dataset on the best model, i.e. CamemBERT + pretraining.
What train/dev/test stragegy ? E.g. trainset 100\% noisy + dev 50\% clean + test 50\% clean ?

@@

\subsection{Implementation details}
we use spacy \mcite{spacy} for the CNN implementation and Huggingface for BERT.

will we use FLAIR as well? $\rightarrow$ No

### 2022-01-09 src-latex/parts/60-results.tex
more details in setup and results

\subsection{Experiment 2: sensibility to training on noisy data}
Idea : Measure the impact of training with noisy data when predicting NER tags on both clean and noisy data.

What's interesting : do models perform better on noisy data when trained on noisy data ? Does it impact predictions on clean data ?

@@

>>>>

@@

\begin{table}
\caption{Camembert vs noise}
\centering
\begin{tabular}{ll|ll|l}
                            &                      & \multicolumn{2}{l|}{Training data} &   \\
                            &                      & noisy & clean                      &   \\ 
\cline{1-4}
\multirow{2}{*}{Test data } & noisy                & f1    & f1                         &   \\
                            & clean                & f1    & f1                         &   \\ 
\cline{1-4}
                            & \multicolumn{1}{l}{} &       & \multicolumn{1}{l}{}       &   \\
                            & \multicolumn{1}{l}{} &       & \multicolumn{1}{l}{}       &  
\end{tabular}
\end{table}
